Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-14 blind.tex
Attempt to wrap up my own sections

We now state our compiler that gives any $\QPIP_0$ protocol blindness.
For the sake of simplicity, we omit the security and accuracy parameters.
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.

\Ethan{Say in words I'm going to compile proto 5 (which is a general form of...) to proto 6}

\Ethan{Add lambda back}

@@

	Common inputs\footnote{TODO something about eps}:
	\begin{itemize}
		\item $x\in\zo^*$
		\item $1^\lambda$
	\end{itemize}

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ correponding to $\Pi_0$}
	Common input: $\lambda$

	Verifier's input: $x\in\zo^*$

	Let $L=\poly(x)$ \Ethan{Quantify/define L more clearly}, $\lambda=\poly(x)$.

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(1^\lambda, \ctx{v}{1}{1}, \ctx{x}{}{1})$
			by evaluating
			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow  \QEval(pk, \cP_1,$ \  $\QEnc(pk_1, 1^\lambda), \ctx{v}{1}{1}, \ctx{x}{}{1})$.
			It sends $\ctx{p}{1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec(sk_{t-1}, \ctx{p}{t-1}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
				by first switching its encryption key;
				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
				then homomorphically decrypts the old encryption by
				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec,$ \ $\ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
				Then it applies the next-message function homomorphically, generating
				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval(pk_t, \cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
				It sends $\ctx{p}{t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec(sk_T, \ctx{p}{T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
	We define $\Hyb_{T+1}$ to be $\Piblind$.
	For $t<T+1$, we define $\Hyb_{t}$ to be the same as $\Hyb_{t+1}$,
	except when $\Vblind$ should send $\ctx{sk}{t}{t}$, it instead sends $\ctx{0}{}{t}$ which is encryption of $0$ under $pk_t$.
	Then, for all $t$, from the perspective of the prover, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
	By a standard hybrid argument, we observe that $\Hyb_1$ is computationally indistinguishable with $\Hyb_{T+1}$.
	Furthermore, $\Hyb_1$ is blind since the prover isn't provided any information about any secret keys.
	\Ethan{do hybrid on 0 too and make sure it fits the dfns. Also should mention why hybriding works}
	So we conclude that $\Piblind$ is blind.
\end{proof}

>>>>

We now state our compiler that gives any $\QPIP_0$ protocol blindness.
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{}{i}$ to denote $x$ encrypted under $pk_i$.
We start with a general form of a $\QPIP_0$ protocol that we'll be compiling.

@@

	Common inputs\footnote{For the sake of simplicity, we omit accuracy parameter $\varepsilon$ where it exists}:
	\begin{itemize}
		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item Some classical input $x\in\zo^*$ \Ethan{Or should this be $\zo^n$? Or $\zo^{\poly(\lambda)}$?}
	\end{itemize}

@@

\begin{protocol}{Blind $\QPIP_0$ protocol $\Piblind=(\Pblind, \Vblind(x))$ correponding to $\Pi_0$}
	Inputs:
	\begin{itemize}
		\item Common input: Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item Verifier's input: $x\in\zo^n$
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $L$ be the maximum circuit depth of $\cP_t$.
	\end{itemize}

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(1^\lambda, x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(1^\lambda, \ctx{v}{1}{1}, \ctx{x}{}{1})$
			by evaluating
			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow  \QEval(pk, \cP_1,$ \  $\QEnc(pk_1, 1^\lambda), \ctx{v}{1}{1}, \ctx{x}{}{1})$.
			It sends $\ctx{p}{1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec(sk_{t-1}, \ctx{p}{t-1}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
				by first switching its encryption key;
				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
				then homomorphically decrypts the old encryption by
				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec,$ \ $\ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
				Then it applies the next-message function homomorphically, generating
				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval(pk_t, \cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
				It sends $\ctx{p}{t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec(sk_T, \ctx{p}{T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	We show that for all cheating prover $P^*$, $\lambda\in\bbN$, $x\in\zo^n$,
	$P^*$ cannot distinguish $(P^*, \Vblind(x))(\lambda)$ from $(P^*, \Vblind(0^n))(\lambda)$ with noticeable probability in $\lambda$.
	We use a hybrid argument; let $\Hyb_{T+1}^x=(P^*, \Vblind(x))(\lambda)$ and $\Hyb_{T+1}^0=(P^*, \Vblind(0^n))(\lambda)$.
	For $2\leq t<T+1$, define $\Hyb_t^x$ to be the same as $\Hyb_{t+1}^x$,
	except when $\Vblind$ should send $\ctx{v}{t}{t}$ and $\ctx{sk}{t-1}{t}$, it instead sends encryptions of $0$ under $pk_t$.
	We define $\Hyb_1^x$ to be the same as $\Hyb_2^x$ except the verifier sends encryptions of $0$ in place of $\ctx{x}{}{1}$ and $\ctx{v}{1}{1}$.
	We define $\Hyb_t^0$ similarly. Note that $\Hyb_1^x$ and $\Hyb_1^0$ are identical.

	For all $t$, from the perspective of the prover,
	as it receives no information on $sk_t$,
	$\Hyb_{t+1}^x$ is computationally indistinguishable from $\Hyb_t^x$ due to the CPA security of $\QHE$ under $pk_t$.
	By a standard hybrid argument, we observe that $\Hyb_1^x$ is computationally indistinguishable with $\Hyb_{T+1}^x$.
	We use the the same argument for the computational indistinguishability between $\Hyb_1^0$ and $\Hyb_{T+1}^0$.
	We conclude that $P^*$ cannot distinguish between $\Hyb_{T+1}^x$ and $\Hyb_{T+1}^0$,
	therefore $\Piblind$ is blind.
\end{proof}

### 2020-04-14 preliminaries.tex
Attempt to wrap up my own sections

\begin{definition}
	A protocol $\Pi=(P, V)$ is said to be in $\QPIP_\tau$ if it satisfies the following properties:
	\begin{itemize}
		\item $P$ is a $\BQP$ \Ethan{wording; quantum poly time?} machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
		\item $V$ is a hybrid machine of a classical part and a limited quantum part. The classical part is a $\BPP$ machine. The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits. At any given time, the verifier is not allowed to possess more than $\tau$ qubits. The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
		\item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially many bits to either direction.
	\end{itemize}
\end{definition}

@@

\begin{definition}
	\label{dfn:stats-secure-proto-sampbqp}
	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
	We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
	\begin{itemize}
		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$. If $d=\Acc$ then $z\in\zo^{m(\abs{x})}$, \footnote{$m$ is the length of... TODO} otherwise $z=\bot$.
		\item (Completeness):
			For all accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
			security parameter $\lambda\in\bbN$,
			and $x\in\zo^{\poly(\lambda)}$, 
			Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\varepsilon}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
		\item (Statistical soundness): For all cheating prover $P^*$,
		    accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
			sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, 
			consider the following experiment:
			\begin{itemize}
				\item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\varepsilon}, x)$.
				\item Define $z_{ideal}$ by
				$$\begin{cases}
					z_{ideal}=\bot & \text{if } d=\Rej\\
					z_{ideal}\leftarrow D_x & \text{if } d=\Acc
				\end{cases}$$.
			\end{itemize}
			It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$. 
		\item (Computational soundness):
		For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
			sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$, 
			define $d, z, z_{ideal}$ by the same experiment as above.
			It holds that
			$$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \varepsilon $$
	\end{itemize}
\end{definition}

@@

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
\begin{definition}
	A quantum homomophic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
	$\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
	\begin{itemize}
		\item \emph{Key generation.}
			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda)$ takes a unary representation of the security parameter as input and outputs a public key $pk$ and a secret key $sk$.
		\item \emph{Encryption.}
			The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ as inputs and outputs a ciphertext $c$.
		\item \emph{Decryption.}
			The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ as inputs and outputs a message $\mu^*\in\zo$.
			It must be the case that
				$$\QDec(sk, \QEnc(pk, \mu))=\mu$$
			with overwhelming probability in $\lambda$.
		\item \emph{Homomorphic Evaluation.}
			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit $f$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ as inputs and outputs a ciphertext $c_f$.
			It must be the case that
				$$\QDec(sk, \QEval(pk, f, c_1, \ldots, c_l))=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))$$
			with overwhelming probability in $\lambda$.
	\end{itemize}
\end{definition}

\begin{definition}[Compactness and Full Homomorphism]
	A quantum homomorphic encryption scheme $\QHE$ is compact if
	there exists a polynomial $s$ in $\lambda$ such that the output length of $\QEval$ is at most $s$ bits long (regardless of $f$ or
	the number of inputs). A compact scheme is (pure) fully homomorphic if it can evaluate any efficiently computable
	boolean function. A compact scheme is leveled fully homomorphic if it takes $1^L$ as additional input in key generation,
	and can only evaluate depth $L$ Boolean circuits where $L$ is polynomial in $\lambda$.
\end{definition}

\Ethan{Combine leveled dfn. with QFHE; keep compactness here}

>>>>

\begin{definition}
	A protocol $\Pi=(P, V)$ is said to be in $\QPIP_\tau$ if it satisfies the following properties:
	\begin{itemize}
		\item $P$ is a $\BQP$ machine, which also has access to a quantum channel that can transmit $\tau$ qubits to the verifier per use.
		\item $V$ is a hybrid machine of a classical part and a limited quantum part. The classical part is a $\BPP$ machine. The quantum part is a register of $\tau$ qubits, on which the verifier can perform arbitrary quantum operations and which has access to a quantum channel which can transmit $\tau$ qubits. At any given time, the verifier is not allowed to possess more than $\tau$ qubits. The interaction between the quantum and classical parts of the verifier is the usual one: the classical part controls which operations are to be performed on the quantum register, and outcomes of measurements of the quantum register can be used as input to the classical part.
		\item There is also a classical communication channel between the prover and the verifier, which can transmit polynomially many bits to either direction.
	\end{itemize}
\end{definition}

@@

\begin{definition}
	\label{dfn:stats-secure-proto-sampbqp}
	Let $\Pi=(P, V)$ be a $\QPIP_\tau$ protocol.
	We say it is a protocol for the $\SampBQP$ instance $(D_x)_{x\in\zo^*}$ with completeness error $c(\cdot)$ and statistical (resp., computational) soundness if the following holds:
	\begin{itemize}
		\item On public inputs $1^\lambda$, $1^{1/\varepsilon}$, and $x\in\zo^{\poly(\lambda)}$, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$. If $d=\Acc$ then $z$ is in the domain \Ethan{?} of $D_x$, otherwise $z=\bot$.
		\item (Completeness):
			For all accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
			security parameter $\lambda\in\bbN$,
			and $x\in\zo^{\poly(\lambda)}$, 
			Let $(d, z)\leftarrow(P, V)(1^\lambda, 1^{1/\varepsilon}, x)$, then $d=\Rej$ with probability at most $c(\lambda)$.
		\item (Statistical soundness): For all cheating prover $P^*$,
		    accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
			sufficiently large $\lambda\in\bbN$, and $x\in\zo^{\poly(\lambda)}$, 
			consider the following experiment:
			\begin{itemize}
				\item Let $(d, z)\leftarrow(P^*, V)(1^\lambda, 1^{1/\varepsilon}, x)$.
				\item Define $z_{ideal}$ by
				$$\begin{cases}
					z_{ideal}=\bot & \text{if } d=\Rej\\
					z_{ideal}\leftarrow D_x & \text{if } d=\Acc
				\end{cases}$$.
			\end{itemize}
			It holds that $\norm{(d,z)-(d,z_{ideal})}_{TV}\leq\varepsilon$. 
		\item (Computational soundness):
		For all cheating $\BQP$ prover $P^*$, $\BQP$ distinguisher $\mathsf{D}$, accuracy parameter $\varepsilon(\lambda)=\frac{1}{\poly(\lambda)}$,
			sufficiently large $\lambda\in\bbN$, and all $x\in\zo^{\poly(\lambda)}$, 
			define $d, z, z_{ideal}$ by the same experiment as above.
			It holds that
			$$\abs{\Pr[\mathsf{D}(1^{\lambda}, d,z) = 1] - \Pr[\mathsf{D}(1^{\lambda}, d,z_{ideal}) = 1]} \leq \varepsilon $$
	\end{itemize}
\end{definition}

@@

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.
\begin{definition}
	A quantum leveled homomophic (public-key) encryption scheme $\QHE=(\QGen,$ \linebreak
	$\QEnc, \QEval, \QDec)$ is quadruple of quantum polynomial-time algorithms which operate as follows:
	\begin{itemize}
		\item \emph{Key generation.}
			The algorithm $(pk, sk)\leftarrow\QGen(1^\lambda, 1^L)$ takes a unary representation of the security parameter and a unary representation of the level parameter as inputs and outputs a public key $pk$ and a secret key $sk$.
		\item \emph{Encryption.}
			The algorithm $c\leftarrow\QEnc(pk, \mu)$ takes the public key $pk$ and a single bit message $\mu\in\zo$ as inputs and outputs a ciphertext $c$.
		\item \emph{Decryption.}
			The algorithm $\mu^*\leftarrow\QDec(sk, c)$ takes the secret key $sk$ and a ciphertext $c$ as inputs and outputs a message $\mu^*\in\zo$.
			It must be the case that
				$$\QDec(sk, \QEnc(pk, \mu))=\mu$$
			with overwhelming probability in $\lambda$.
		\item \emph{Homomorphic Evaluation.}
			The algorithm $c_f\leftarrow\QEval(pk, f, c_1, \ldots, c_l)$ takes the public key $pk$, a quantum circuit $f$ of depth at most $L$, and a set of $l$ ciphertexts $c_1,\cdots,c_l$ as inputs and outputs a ciphertext $c_f$.
			It must be the case that
				$$\QDec(sk, \QEval(pk, f, c_1, \ldots, c_l))=f(\QDec(sk, c_1),\ldots,\QDec(sk, c_l))$$
			with overwhelming probability in $\lambda$.
	\end{itemize}
\end{definition}

\begin{definition}[Compactness and Full Homomorphism]
	A quantum homomorphic encryption scheme $\QHE$ is compact if
	there exists a polynomial $s$ in $\lambda$ such that the output length of $\QEval$ is at most $s$ bits long (regardless of $f$ or
	the number of inputs). A compact scheme is (pure) fully homomorphic if it can evaluate any efficiently computable
	boolean function.
\end{definition}
